Transparent Changes

### 2022-04-02 scripts/review.Rmd
Analyse abstract screen, prepare fulltext screen

sampled_data[500,]

@@

>>>>

@@

#### Compare abstract screening results

```{r abstract-screen}
load("../data/screen/sample.Rda")
# read screening results
s_res1 <- read.csv("../data/screen/abstract_screening_i1.csv")[, 2]
s_res2 <- read.csv("../data/screen/abstract_screening_i2.csv")[, 2]

# compare results
comp_res <- function(x1, x2) {
  if (is.na(x1)) x1c <- 0 else x1c <- x1
  if (is.na(x2)) x2c <- 0 else x2c <- x2
  if (x1c == x2c) out <- x1 else out <- "XXX"
  out
}

s_res <- purrr::map2_chr(s_res1, s_res2, comp_res)
s_res_df <- data.frame(
  id = 1:500,
  i1 = s_res1,
  i2 = s_res2,
  result = s_res,
  decision = rep.int("", 500),
  doi = sampled_data$doi
)
# write.csv(s_res_df, "../data/screen/abstract_screening.csv")
# Calculate relative agreement
1 - (sum(s_res == "XXX", na.rm = TRUE) / length(s_res))

# Get final decisions
s_res_final <- read.csv("../data/screen/abstract_screening.csv")
# number excluded 
sum(!is.na(s_res_final$decision))
# extract remaining data
ft_screen <- sampled_data[is.na(s_res_final$decision), ]

l <- list.files("../data/fulltext")
get_ft_id <- function(n, files) {
  name <- files[n]
  as.numeric(strsplit(name, "\\.")[[1]][[1]])
}
fts <- purrr::map_dbl(seq_along(l), get_ft_id, files = l)
# find missing full texts
# ft_screen$sid[!ft_screen$sid %in% fts]

# write file for full text screening
ft_screen_df <- data.frame(
  sid = ft_screen$sid,
  fulltext_exclusion = rep.int("", nrow(ft_screen)),
  exclusion_note = rep.int("", nrow(ft_screen)),
  doi = ft_screen$doi
)
# write.csv(ft_screen_df, file = "../data/screen/fulltext_screening_i1.csv", row.names = FALSE)
```
